\plaintitle

### 2015-11-07 Paper/paper.tex
Added draft for Methodology

@@

>>>>

\subsubsection{Cross-Site HTTP Requests}

The system will be designed to support HTTP Requests from specific domains
where the frontend code will be stored. This is to be able to outsource the load
added by frontend data being served as it will take a significant amount of
networking bandwidth to serve the images and scripts included. This will also
allow the frontend to have heavier images and scripts without affecting the 
performance of the main server.

@@

The frontend will be a static web application that fires REST requests to the
server. The Javascript Object Notation (JSON) will be used to specify parameters
for commands that require sending non-anonymous data while a normal GET request
can be used for reading data. The frontend will also have an enlistment queue
where the user can setup which subjects he/she would like to enlist and then
send them as a batch to the server. This would lessen the number of connections
that the server will receive lessening the number of threads running in the 
backend.
